Combinatorics of the geometry of Wilson loop diagrams

### 2019-01-01 General WLD combinatorics.tex
addressed a few comments from the last meeting

\begin{dfn} \label{VPropdfn}
Let $W = (\cP, [n])$.
\begin{enumerate}
\item For $p \in \cP$, let $V(p) = \{i_p, i_p+1, j_p, j_p+1\}$ be the set of vertices supporting $p$. Then, for $P \subseteq \cP$, the set $V(P) = \cup_{p \in P} V(p)$ is the vertex support of $P$.
\item For $V \subseteq [n]$, write $\Prop(V) = \{ p \in \cP | V(p) \cap V \neq \emptyset \} $.
\item For $P \subseteq \cP$, define $F(P) = V(P^c)^c$ to be the set of vertices in $[n]$ that do not support any propagators outside the set $P$.
\end{enumerate}
\end{dfn}

Note that $F(\emptyset)$ is the set of vertices that are not in the support of any propagators. \note{mention that $F(\emptyset)$ is also called nonsupporting and also phrase as a note that old lemma about $F(P) = stuff - stuff$.}

@@

Note that this means that the set $F(\emptyset)$ is the maximal subset of vertices of $W$ of rank $0$. That is, it is the unique flat of rank $0$ in $M(W)$. \sanote{I'm sprinkling comments about $F(\emptyset)$ throughout until we can come up with a better name than unsupportive vertices.}

@@

\begin{lem} \label{lem decompose flat}Let $F$ be a flat in $M(W)$, and let $C \subseteq F$ be the union of all circuits contained in $F$. Then the following are true:
\begin{enumerate}
\item $C = F(\Prop (C))$, i.e. $C$ is a propagator flat.
\item $F \setminus C$ is an independent  flat.  
\end{enumerate}
\end{lem}

@@

\note{the one element could be e so this doesn't work}
For any $e \not\in F$, we certainly have $\rk((F\setminus C)\cup\{e\}) = \rk(F\setminus C) +1$ since $F$ is a flat. Now let $e \in C$, and suppose that $\rk((F\setminus C)\cup\{e\}) = \rk(F\setminus C)$. This implies that $(F\setminus C)\cup \{e\}$ is dependent, and hence contains a circuit, $S$. This circuit must contain at least one element but this contradicts the fact that $C$ was the union of all circuits in $F$.

>>>>

\begin{dfn} \label{VPropdfn}
Let $W = (\cP, [n])$.
\begin{enumerate}
\item For $p \in \cP$, let $V(p) = \{i_p, i_p+1, j_p, j_p+1\}$ be the set of vertices supporting $p$. Then, for $P \subseteq \cP$, the set $V(P) = \cup_{p \in P} V(p)$ is the vertex support of $P$.
\item For $V \subseteq [n]$, write $\Prop(V) = \{ p \in \cP | V(p) \cap V \neq \emptyset \} $.
\item For $P \subseteq \cP$, define $F(P) = V(P^c)^c$ to be the set of vertices in $[n]$ that do not support any propagators outside the set $P$.
\item The set of vertices that are not in the support of any propagotors is denoted  $F(\emptyset)$. Vertices in this set are called non-supporting.  
\end{enumerate}
\end{dfn}

\begin{rmk}\label{alt F(P) rmk}
Note that a more explicit definition of $F(P)$ is \bas F(P)  = \big(V(P) \setminus V(P^c) \big) \cup F(\emptyset) \eas
\end{rmk}

@@

Note that this means that the set, $F(\emptyset)$, of non-supporting vertices is the maximal subset of vertices of $W$ of rank $0$. That is, it is the unique flat of rank $0$ in $M(W)$.

@@

\begin{lem} \label{lem decompose flat}Let $F$ be a flat in $M(W)$, and let $C \subseteq F$ be the union of all circuits contained in $F$. Then the following are true:
\begin{enumerate}
\item $C = F(\Prop (C))$, i.e. $C$ is a propagator flat.
\item $F \setminus C$ is an independent set. Furthermore, If $F\setminus C$ is an independent flat if and only if $F(\emptyset) = \emptyset$, that is $W$ has no non-supporting vertices.  
\end{enumerate}
\end{lem}

@@

Note that since $F(\emptyset)$ has rank $0$, $F(\emptyset)$ is contained in every flat of $W$. Therefore, if $F(\emptyset) \neq \emptyset$, then $F\setminus C$ cannot be a flat.

If $F(\emptyset) = \emptyset$, for any $e \not\in F$, we certainly have $\rk((F\setminus C)\cup\{e\}) = \rk(F\setminus C) +1$ since $F$ is a flat. Now let $e \in C$, and suppose that $\rk((F\setminus C)\cup\{e\}) = \rk(F\setminus C)$. This implies that $(F\setminus C)\cup \{e\}$ is dependent, and hence contains a circuit, $S$. Since $F(\emptyset) = \emptyset$, this circuit must contain at least two elements but this contradicts the fact that $C$ was the union of all circuits in $F$.
